Data preparation

### 2020-10-03 production/prod_prep-data.rmd
ajustes finales data-prerp y analisis

```{r}
plot_likert((getahead[,3:8]), 
                        geom.colors   = c("#9ecae1", "#6baed6","#4292c6", 
                                            "#2171b5"), # colorbrewer2.org 
                        sort.frq      = "neg.asc", # sort descending)
                        title         = "getahead",
                        intercept.line.color = "white", # vertical middle
                        expand.grid   = F, # no inner margins in plot
                        show.n        = FALSE, # hide N's in axis labels
                        grid.range    = 1.8,
                        geom.size = 0.6) # expand axis 130% )
```

@@

```{r}
before_detearn<-sjPlot::plot_likert(detearn[,3:8],
                    geom.colors   = c("#9ecae1", "#6baed6", "#4292c6", "#2171b5"), # colorbrewer2.org
                    cat.neutral = 3,
                    sort.frq      = "neg.asc", # sort descending)
                    title         = "Before detearn",
                    intercept.line.color = "white", # vertical middle
                    expand.grid   = F, # no inner margins in plot
                    show.n        = FALSE, # hide N's in axis labels
                    grid.range    = 1.8,
                    geom.size = 0.6) # expand axis 130% ))

@@

```{r}

@@

save(after_detearn, file="output/images/after_detearn.png")

@@

 - 
Estimation of the model c / unmerit 2nd order
 - 
Estimation of the model c / unmerit 2nd order

@@

Two ways of calculating the redistribution variable at the country level are presented below. Both proportionally equivalent.
   - Calculation according to Bradley[(2003)](https://www.jstor.org/stable/25054218?seq=1) __(net gini / gini mkt)*100__
   - Calculation used by Solt in [SWIID](https://fsolt.org/swiid/) __(gini mkt - gini net)/gini mkt__

>>>>

```{r likert-getahead}
plot_likert((getahead[,3:8]), 
                        geom.colors   = c("#9ecae1", "#6baed6","#4292c6", 
                                            "#2171b5"), # colorbrewer2.org 
                        sort.frq      = "neg.asc", # sort descending)
                        title         = "getahead",
                        intercept.line.color = "white", # vertical middle
                        expand.grid   = F, # no inner margins in plot
                        show.n        = FALSE, # hide N's in axis labels
                        grid.range    = 1.8,
                        geom.size = 0.6) # expand axis 130% )
```

@@

```{r likert-detearn-before}
before_detearn<-sjPlot::plot_likert(detearn[,3:8],
                    geom.colors   = c("#9ecae1", "#6baed6", "#4292c6", "#2171b5"), # colorbrewer2.org
                    cat.neutral = 3,
                    sort.frq      = "neg.asc", # sort descending)
                    title         = "Before detearn",
                    intercept.line.color = "white", # vertical middle
                    expand.grid   = F, # no inner margins in plot
                    show.n        = FALSE, # hide N's in axis labels
                    grid.range    = 1.8,
                    geom.size = 0.6) # expand axis 130% ))
before_detearn

@@

```{r likert-detearn-after}

@@

save(after_detearn, file="output/images/after_detearn.png")
after_detearn
```

@@

 - 
Estimation of the model c / unmerit 2nd order

@@

Two ways of calculating the redistribution variable at the country level are presented below. Both proportionally equivalent.

   +  Calculation according to Bradley[(2003)](https://www.jstor.org/stable/25054218?seq=1) __(net gini/gini mkt)*100__

   + Calculation used by Solt in [SWIID](https://fsolt.org/swiid/) __(gini mkt - gini net)/gini mkt__
